\subsection{Sketch Class Reference}
\label{subsec:sketch_wearable}\mbox{}

    \paragraph{Public Attributes}\mbox{}\\

        \begin{itemize}
            \item String \textbf{message}
            
                \quad \quad \textit{A copy of the message received from the walking aid device.}

            \item uint8\_t \textbf{broadcastAddress[]}
            
                \quad \quad \textit{The MAC address of the walking aid device.}

            \item WearableAccelerometer \textbf{accel}

            \item WearableCommunications \textbf{comms}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item void \textbf{OnDataRecv}(const uint8\_t * mac, const uint8\_t *data, int len) 
            
                \quad \quad \textit{Callback function to be executed when data is received from a vibrate message.}

            \item void \textbf{setup}() 
            
                \quad \quad \textit{Handles the initialisation of the accelerometer and the communications objects and is the }

                \quad \quad \textit{Arduino setup function.}


            \item void \textbf{loop}() 
            
                \quad \quad \textit{Calls the poll accelerometer function and calls to send a message to the walking aid device if }
                
                \quad \quad \textit{the poll function returns true. Acts as the Arduino loop function.}\\
        \end{itemize}


    \subsubsection{Member Function Documentation}\mbox{}

        \paragraph{OnDataRecv()}\mbox{}\\

            \ttfamily{void OnDataRecv (\\
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const uint8\_t * mac,\\ 
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const uint8\_t *data,\\ 
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad int len)}\\

            \rmfamily{Callback function to be executed when data is received from a vibrate message.}

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                mac & MAC address of the device that sent the vibrate message.\\ 
                \hline
                data & Data of the vibrate message.\\ 
                \hline
                len & Length of the vibrate message.\\ 
                \hline
            \end{tabular}\\~\\

        \paragraph{setup()}\mbox{}\\

            \ttfamily{void setup (  )}\\

            \rmfamily{Handles the initialisation of the accelerometer and the communications objects and is the Arduino setup }

            function.


        \paragraph{loop()}\mbox{}\\

            \ttfamily{void loop (  )}\\

            \rmfamily{Calls the poll accelerometer function and calls to send a message to the walking aid device if the poll }
            
            function returns true. Acts as the Arduino loop function.\\