\subsection{WearableCommunications Class Reference}
\label{subsec:WearableCommunications}\mbox{}

    \ttfamily{}

    \#include <WearableCommunications.h>\\

    \rmfamily{}

    \paragraph{Private Attributes}\mbox{}\\

        \begin{itemize}
            \item String \textbf{message}
            
                \quad \quad \textit{The message to send to the peer.}
                
            \item uint8\_t \textbf{*broadcastAddress}
            
                \quad \quad \textit{The MAC address of the peer.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item \textbf{WearableCommunications}() 
            
                \quad \quad \textit{Construct a new Wearable Communications object.}

            \item void \textbf{init}(String message, uint8\_t broadcastAddress[])
            
                \quad \quad \textit{Initialise ESP-Now and peer device info, and set on send message callback function.}
                
            \item void \textbf{sendReminderMessage}() 
            
                \quad \quad \textit{Send the message to the walking aid device.}\\

        \end{itemize}

    \subsubsection{Constructor \& Destructor Documentation}\mbox{}


        \paragraph{WearableCommunications()}\mbox{}\\

            \ttfamily{WearableCommunications::WearableCommunications (  )}\\

            \rmfamily{Construct a new Wearable Communications object.}\\


    \subsubsection{Member Function Documentation}\mbox{}


        \paragraph{init()}\mbox{}\\

            \ttfamily{void WearableCommunications::init (\\
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad String message,\\ 
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad uint8\_t broadcastAddress[])}\\

            \rmfamily{Initialise ESP-Now and peer device info, and set on send message callback function.}\\

        \paragraph{sendReminderMessage()}\mbox{}\\

            \ttfamily{bool WearableCommunications::getReminder (  )}\\

            \rmfamily{Send the message to the walking aid device.}\\