\subsection{SDToSPIFFS Class Reference}
\label{subsec:sdtospiffs}\mbox{}

    \ttfamily{}

    \#include <SDToSPIFFS.h>\\

    \rmfamily{}

    \paragraph{Private Attributes}\mbox{}\\

        \begin{itemize}
            \item const char * \textbf{SDPath}
            
                \quad \quad \textit{Audio file to be transferred.}

            \item const char * \textbf{SPIFFSPath}
            
                \quad \quad \textit{Name to give the audio file being saved in SPIFFS.}

            \item SdFat \textbf{sd}
            
                \quad \quad \textit{SD Card object.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item \textbf{SDToSPIFFS}() 
            
                \quad \quad \textit{Construct a new SDToSPIFFS object.}

            \item void \textbf{init}(const char *SDPath, const char* SPIFFSPath) 
            
                \quad \quad \textit{Initalises the object ready for the transferring of files from SD card to SPIFFS.}

            \item void \textbf{loadSDFileToSPIFFS}() 
            
                \quad \quad \textit{Handles the loading of the SD card file to SPIFFS.}

            \item const char *\textbf{getSPIFFSPath}() 
            
                \quad \quad \textit{Returns the path to the SPIFFS file.}\\
        \end{itemize}

    \subsubsection{Constructor \& Destructor Documentation}\mbox{}


        \paragraph{SDToSPIFFS()}\mbox{}\\

            \ttfamily{SDToSPIFFS::SDToSPIFFS (  )}\\

            \rmfamily{Construct a new SDToSPIFFS object.}\\


    \subsubsection{Member Function Documentation}\mbox{}


        \paragraph{init()}\mbox{}\\

            \ttfamily{void SDToSPIFFS::init (\\
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const char * SDPath,\\ 
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const char * SPIFFSPath )}\\

            \rmfamily{Initialises the object ready for the transferring of files from SD card to SPIFFs.}

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                SDPath & The path to the SD card file. \\ 
                \hline
                SPIFFSPath & The file name to give the new SPIFFS file. \\ 
                \hline
            \end{tabular}\\~\\


        \paragraph{loadSDFileToSPIFFS()}\mbox{}\\

            \ttfamily{void SDToSPIFFS::loadSDFileToSPIFFS (  )}\\

            \rmfamily{Handles the loading of the SD card file to SPIFFS.}\\


        \paragraph{getSPIFFSPath()}\mbox{}\\

            \ttfamily{const char * SDToSPIFFS::getSPIFFSPath (  )}\\

            \rmfamily{Returns the path to the SPIFFS file.}

            \textbf{Returns}

                \quad \quad const char* SPIFFS file path.\\