\subsection{Sketch Class Reference}
\label{subsec:sketch_walking_aid}\mbox{}

    \paragraph{Public Attributes}\mbox{}\\

        \begin{itemize}
            \item String \textbf{message}
            
                \quad \quad \textit{A copy of the message received from the wearable device.}

            \item uint8\_t \textbf{broadcastAddress[]}
            
                \quad \quad \textit{The MAC address of the wearable device.}

            \item WalkAidAudio \textbf{audio}
            
                \quad \quad \textit{The audio controller object.}

            \item WalkAidCommunications \textbf{comms}
            
                \quad \quad \textit{The communications controller object.}
                
            \item WalkAidAccelerometer \textbf{accel}
            
                \quad \quad \textit{The accelerometer controller object.}
                
            \item WalkAidAccelerometer \textbf{accel}
            
                \quad \quad \textit{Should the wearable device vibrate or not.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item void \textbf{OnDataRecv}(const uint8\_t * mac, const uint8\_t *data, int len) 
            
                \quad \quad \textit{Callback function to be executed when data is received from a reminder message.}

            \item void \textbf{setup}() 
            
                \quad \quad \textit{Handles the Arduino setup function. Initialises the accelerometer, communications, and audio.}

            \item void \textbf{loop}() 
            
                \quad \quad \textit{Handles the Arduino loop function. Loops through checks for reminder messages and responds }
                
                \quad \quad \textit{accordingly.}\\
        \end{itemize}


    \subsubsection{Member Function Documentation}\mbox{}

        \paragraph{OnDataRecv()}\mbox{}\\

            \ttfamily{void OnDataRecv (\\
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const uint8\_t * mac,\\ 
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const uint8\_t *data,\\ 
            \null \quad \quad \quad \quad \quad \quad \quad \quad \quad int len)}\\

            \rmfamily{Callback function to be executed when data is received from a vibrate message.}

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                mac & MAC address of the device that sent the reminder.\\ 
                \hline
                data & Data of the reminder.\\ 
                \hline
                len & Length of the reminder.\\ 
                \hline
            \end{tabular}\\~\\


        \paragraph{setup()}\mbox{}\\

            \ttfamily{void setup (  )}\\

            \rmfamily{Handles the Arduino setup function. Initialises the accelerometer, communications, and audio.}


        \paragraph{loop()}\mbox{}\\

            \ttfamily{void loop (  )}\\

            \rmfamily{Handles the Arduino loop function. Loops through checks for reminder messages and responds }
            
            accordingly.\\