\subsection{WalkAidAudio Class Reference}
\label{subsec:WalkAidAudio}\mbox{}

    \ttfamily{}

    \#include <WalkAidAudio.h>\\

    \rmfamily{}

    \paragraph{Private Attributes}\mbox{}\\

        \begin{itemize}
            \item AudioGeneratorMP3 * \textbf{mp3}
            
                \quad \quad \textit{The generator of the mp3 player.}

            \item AudioFileSourceSPIFFS * \textbf{file}
            
                \quad \quad \textit{The source file of the SPIFFS audio file.}

            \item AudioOutputI2S * \textbf{out}
            
                \quad \quad \textit{The output of the mp3 player.}

            \item AudioFileSourceID3 * \textbf{id3}
            
                \quad \quad \textit{Metadata handler for the mp3 file.}

            \item SDToSPIFFS \textbf{s2s}
            
                \quad \quad \textit{Object to handle the SD to SPIFFS transfer.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item \textbf{WalkAidAudio}() 
            
                \quad \quad \textit{Construct a new Walk Aid Audio object.}

            \item void \textbf{init}(const char *SDPath, const char *SPIFFSPath) 
            
                \quad \quad \textit{Initialises the accelerometer with the specified values in parameter fields.}

            \item void \textbf{play}() 
            
                \quad \quad \textit{Plays the SPIFFS audio file.}\\

        \end{itemize}

    \subsubsection{Constructor \& Destructor Documentation}\mbox{}


        \paragraph{WalkAidAudio()}\mbox{}\\

            \ttfamily{WalkAidAudio::WalkAidAudio (  )}\\

            \rmfamily{Construct a new Walk Aid Audio object.}\\


    \subsubsection{Member Function Documentation}\mbox{}


        \paragraph{init()}\mbox{}\\

            \ttfamily{void WalkAidAudio::init (\\
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const char * SDPath,\\ 
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad const char * SPIFFSPath)}\\

            \rmfamily{Initialises the walk aid audio system by calling the transfer of SD file to SPIFFS and generating the}

            mp3 code.

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                SDPath & Path to the SD card audio file.\\ 
                \hline
                SPIFFSPath & Name of the SPIFFS audio file to be created.\\ 
                \hline
            \end{tabular}\\~\\


        \paragraph{play()}\mbox{}\\

            \ttfamily{void WalkAidAudio::play (  )}\\

            \rmfamily{Plays the SPIFFS audio file.}\\