\subsection{WalkAidCommunications Class Reference}
\label{subsec:WalkAidCommunications}\mbox{}

    \ttfamily{}

    \#include <WalkAidCommunications.h>\\

    \rmfamily{}

    \paragraph{Private Attributes}\mbox{}\\

        \begin{itemize}
            \item bool \textbf{reminder}
            
                \quad \quad \textit{Whether a reminder message has been received.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item \textbf{WalkAidCommunications}() 
            
                \quad \quad \textit{Construct a new Walk Aid Communications object.}

            \item void \textbf{init}()
            
                \quad \quad \textit{Initialise communication to the wearable device.}

            \item bool \textbf{getReminder}() 
            
                \quad \quad \textit{Get whether a reminder has been received or not.}
                
            \item void \textbf{setReminder}(bool reminder) 
            
                \quad \quad \textit{Set whether a reminder has been received or not.}\\

        \end{itemize}

    \subsubsection{Constructor \& Destructor Documentation}\mbox{}


        \paragraph{WalkAidCommunications()}\mbox{}\\

            \ttfamily{WalkAidCommunications::WalkAidCommunications (  )}\\

            \rmfamily{Construct a new Walk Aid Communications object.}\\


    \subsubsection{Member Function Documentation}\mbox{}


        \paragraph{init()}\mbox{}\\

            \ttfamily{void WalkAidCommunications::init ()}\\

            \rmfamily{Initialise communication to the wearable device.}

        \paragraph{getReminder()}\mbox{}\\

            \ttfamily{bool WalkAidCommunications::getReminder (  )}\\

            \rmfamily{Get whether a reminder has been received or not.}

            \textbf{Returns}

                \quad \quad bool reminder.\\


        \paragraph{setReminder()}\mbox{}\\

            \ttfamily{void WalkAidCommunications::setReminder (  )}\\

            \rmfamily{Set whether a reminder has been received or not.}

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                reminder & true if reminder received, false otherwise.\\ 
                \hline
            \end{tabular}\\~\\