\subsection{WalkAidAccelerometer Class Reference}
\label{subsec:WalkAidAccelerometer}\mbox{}

    \ttfamily{}

    \#include <WalkAidAccelerometer.h>\\

    \rmfamily{}

    \paragraph{Private Attributes}\mbox{}\\

        \begin{itemize}
            \item double \textbf{singleTapThresholdValue}
            
                \quad \quad \textit{Threshold for single tap to be detected.}

            \item double \textbf{singleTapThresholdDuration}
            
                \quad \quad \textit{Duration for single tap to be above threshold to be detected.}

            \item double \textbf{doubleTapLatency}
            
                \quad \quad \textit{Time between a tap event and when the reading for a double tap starts.}

            \item double \textbf{doubleTapWindow}
            
                \quad \quad \textit{Defines how long a double tap is checked for.}

            \item bool \textbf{stepDetected}
            
                \quad \quad \textit{Defines if a step has been detected.}

            \item long \textbf{lastStepTime}
            
                \quad \quad \textit{The last time a step was detected.}

            \item unsigned long \textbf{period}
            
                \quad \quad \textit{The period to check previously and in future for detected steps.}

            \item ADXL345 \textbf{adxl}
            
                \quad \quad \textit{Accelerometer object.}\\

        \end{itemize}


    \paragraph{Public Member Functions}\mbox{}\\

        \begin{itemize}
            \item \textbf{WalkAidAccelerometer}() 
            
                \quad \quad \textit{Construct a new Walk Aid Accelerometer object.}

            \item void \textbf{init}(double singleTapThresholdValue, double singleTapThresholdDuration
            , \\double doubleTapLatency, double doubleTapWindow, unsigned long period) 
            
                \quad \quad \textit{Initialises the accelerometer with the specified values in parameter fields.}

            \item bool \textbf{checkForStep}() 
            
                \quad \quad \textit{Checks if a tap event was detected by the accelerometer.}

            \item bool \textbf{isStepDetected}() 
            
                \quad \quad \textit{Returns the value of stepDetected.}

            \item long \textbf{getLastStepTime}() 
            
                \quad \quad \textit{Get the time the last step was taken.}

            \item unsigned long \textbf{getPeriod}() 
            
                \quad \quad \textit{Get the developer's specified period to check for steps.}\\

        \end{itemize}

    \subsubsection{Constructor \& Destructor Documentation}\mbox{}


        \paragraph{WalkAidAccelerometer()}\mbox{}\\

            \ttfamily{WalkAidAccelerometer::WalkAidAccelerometer (  )}\\

            \rmfamily{Construct a new Walk Aid Accelerometer object.}\\


    \subsubsection{Member Function Documentation}\mbox{}


        \paragraph{init()}\mbox{}\\

            \ttfamily{void WalkAidAccelerometer::init (\\
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad double singleTapThresholdValue,\\ 
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad double singleTapThresholdDuration,\\ 
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad double doubleTapLatency,\\
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad double doubleTapWindow,\\
                \null \quad \quad \quad \quad \quad \quad \quad \quad \quad unsigned long period)}\\

            \rmfamily{Initialises the accelerometer with the specified values in parameter fields.}

            \textbf{Parameters}

            \vspace{1em}
            \begin{tabular}{| l | l |} 
                \hline
                singleTapThresholdValue & Threshold for single tap to be detected.\\ 
                \hline
                singleTapThresholdDuration & Duration that tap must be above threshold to be detected.\\ 
                \hline
                doubleTapLatency & Time after single tap until double tap is measured.\\ 
                \hline
                doubleTapWindow & How long double tap is checked for.\\ 
                \hline
                period & Time period to check for steps before and after receiving message.\\ 
                \hline
            \end{tabular}\\~\\


        \paragraph{checkForStep()}\mbox{}\\

            \ttfamily{bool WalkAidAccelerometer::checkForStep (  )}\\

            \rmfamily{Checks if a tap event was detected by the accelerometer.}\\

            \textbf{Returns}

                \quad \quad true if tap is detected, false otherwise.\\


        \paragraph{isStepDetected()}\mbox{}\\

            \ttfamily{bool WalkAidAccelerometer::isStepDetected (  )}\\

            \rmfamily{Returns the value of stepDetected.}

            \textbf{Returns}

                \quad \quad bool stepDetected\\

        \paragraph{getLastStepTime()}\mbox{}\\

            \ttfamily{long WalkAidAccelerometer::getLastStepTime (  )}\\

            \rmfamily{Get the time the last step was taken.}

            \textbf{Returns}

                \quad \quad long lastStepTime.\\

        \paragraph{getPeriod()}\mbox{}\\

            \ttfamily{unsigned long WalkAidAccelerometer::getPeriod (  )}\\

            \rmfamily{Get the developer's specified period to check for steps.}

            \textbf{Returns}

                \quad \quad unsigned long period.\\