\chapter{Specification}\label{ch:specification}

    In this chapter, we'll go through the project in further depth. More specifically, we will outline a proposed
    solution as well as describing the product.

    \section{Description}

        The challenge of this project is to develop an effective system that interacts with users, who are dementia
        patients. This project will support the development of a wearable device including an application. The dementia
        patient or user will be encouraged to use the walking assistance in this application. A recorded message from a
        family member or relative will act as the notification. The device will detect if the user is sleeping and if is
        not, the device will only then be activated, since we do not want the device to begin notifying the user while
        he is sleeping, as the user might be startled by the notice.

        The user does not need to log in or register with the system since the device will obtain the necessary data
        through an SD card, such as the familiar voice of a relative or family member. Although dementia patients may be
        deaf, the wearable device will support a solution for deaf individuals, such as reminding them to take their
        walking aid with them without utilising any audio, such as a slight vibration.

    \section{Software behaviors}

        The wearable device must communicate with the walking aid device in order for all of this to be happen. This
        communication, can be happened by using a transmitter. As soon as movement is detected, the transmitter will
        send message to the wearable device, letting it know that the user started walking. In this way the wearable
        device will be able to tell when the patient has used the walking aid and is actually walking. Otherwise, as
        mentioned before a message will be played to remind the patient to take their walking aid with them. The device
        will cease warning the user once the system detects that the user has used the walking aid and begun walking.

        Furthermore, dementia all types of people at varying ages. That means that the wearable device must be able to
        fit on anyone's wrist. Because we do not want patients to feel uncomfortable while using the wearable device, it
        will be designed to look like a watch. That means that the user, who in this case is a dementia patient, will
        not interact with the watch, by any means of having to select an option on the device or even to change a
        setting. Apart from the device's appearance and dimensions, the device should be power efficient, as the
        patients most of the time will forget to charge it.

        The device will also include a fall detection functionality. If the development time allows, we will integrate
        this capability into the device. A tri axial accelerometer will be used to determine the user's hand height, and
        more particularly the device's height. If the user's hand is extremely close to the ground, it is likely that
        the user has fallen. If the device detects that the user has been on the ground for an extended amount of time,
        it will begin informing a relative or a nearby caregiver.
